|

### 2019-07-18 README.Rmd
Remove text from manscript.Rmd
Update github READMEs

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and Rho GTPases. _Molecular and Cellular_ 
_Proteomics_, submitted.

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Research compendium for "Protein markers for 
_Candida albicans_ EVs include claudin-like Sur7 family proteins and Rho 
GTPases". version x.x.x. Zenodo. URL.

@@

```
    .
    ├── /R                   # Script files for functions and included data
    ├── /data-raw            # Raw data used (but not modified) in analyses
    ├── /data                # Data tables installed with package
    ├── /inst/manuscript     # Final submitted manuscript and supplemental files
    ├── /man                 # Auto-generated documentation for functions and included data
    ├── /vignettes           # Detailed examples of how analyses were performed
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitattributes       # List of files for github/linguist to ignore
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # Rmarkdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

@@

This research compendium can be installed as an R package `candidaev` from 
GitHub using `devtools`. A full installation will include all the functions and 
data included in the package as well as some HTML vignettes,
and the manuscript `.Rmd` file which can be used to reproduce the manuscript as
it was submitted.

@@

**Note:** the contents of `/data-raw` and `/inst/manuscript/supplement_files` 
are not installed when the package is 
installed using `install_github`. Instead, `/data-raw` can be manually 
downloaded from 
[here](https://github.com/csdaw/candidaev/tree/master/data-raw) and 
`/inst/manuscript/supplement_files` can be manually downloaded from 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

@@

The manuscript `.pdf` file, as submitted, can be downloaded 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

#### Building the manuscript from scratch

To generate the reproducible manuscript, an installation of LaTeX is required. 
TinyTex is a good option for this and can be installed using:

@@

Then the manuscript (and supplement) can be built using:

```{r, eval=FALSE}
# requires LaTeX installation and full compendium installation
rmarkdown::render(system.file("manuscript", "manuscript.Rmd", 
                              package = "candidaev"))
rmarkdown::render(system.file("manuscript", "manuscript_supplement.Rmd", 
                              package = "candidaev"))
```

@@

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

>>>>

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and GTPases. _Journal of Extracellular_ 
_Vesicles_, submitted.

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Research compendium for "Protein markers for 
_Candida albicans_ EVs include claudin-like Sur7 family proteins and GTPases". 
version x.x.x. Zenodo. URL.

@@

```
    .
    ├── /R                   # Script files for functions and included data
    ├── /data-raw            # Raw data used (but not modified) in analyses
    ├── /data                # Data tables installed with package
    ├── /inst/manuscript     # Final submitted manuscript, figures, and supplementary data
    ├── /man                 # Auto-generated documentation for functions and included data
    ├── /vignettes           # Detailed examples of how analyses were performed
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitattributes       # List of files for github/linguist to ignore
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # Rmarkdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

@@

This research compendium can be installed as an R package `candidaev` from 
GitHub using `devtools`. A full installation will include all the functions and 
data included in the package as well as some HTML vignettes, the manuscript
text, the figures `.Rmd` file which can be used to reproduce the analysis and 
figures as submitted.

@@

**Note:** the contents of `/data-raw` and `/inst/manuscript/supplementary_data` 
are not installed when the package is 
installed using `install_github`. Instead, `/data-raw` can be manually 
downloaded from 
[here](https://github.com/csdaw/candidaev/tree/master/data-raw) and 
`/inst/manuscript/supplementary_data` can be manually downloaded from 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

@@

The manuscript `.docx` file, as submitted, can be downloaded 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

The figures for the manuscript were produced using the `candidaev_figures.Rmd` 
file which can be downloaded
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

#### Building the figures from scratch

To generate the reproducible figures, an installation of LaTeX is required. 
TinyTex is a good option for this and can be installed using:

@@

Then the manuscript figures (and supplement) can be built using:

```{r, eval=FALSE}
# requires LaTeX installation and full compendium installation
rmarkdown::render(system.file("manuscript", "candidaev_figures.Rmd", 
                              package = "candidaev"))
rmarkdown::render(system.file("manuscript", "candidaev_supplement.Rmd", 
                              package = "candidaev"))
```

@@

```{r sessionInfo, echo=FALSE, cache=FALSE}
devtools::session_info()
```

### 2019-07-18 inst/manuscript/README.Rmd
Update github READMEs

This directory contains the submitted manuscript, supplemental figures and 
tables, and supplemental files for our paper:

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
submitted.

@@

## Contents
```
    .
    ├── ...
    ├── /inst
    │    ├── /manuscript
    │         ├── /components                 # Contains required components for building the manuscript
    │         ├── /figures                    # Contains .svg and .csv files used to make some figures
    │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
    │         ├── manuscript.Rmd              # R markdown file to produce manuscript.pdf
    │         ├── manuscript.pdf              # Final submitted manuscript
    │         ├── manuscript_supplement.Rmd   # R markdown file to produce manuscript_supplement.pdf
    │         ├── manuscript_supplement.pdf   # Final submitted supplemental figures and tables
    │         ├── README.Rmd                  # R markdown file to produce README.md
    │         └── README.md                   # Description of /inst/manuscript directory
    └── ...

>>>>

This directory contains the submitted manuscript `.docx` file, main figures,
supplementary figures, and supplementary data for our paper:

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and GTPases. _Journal of Extracellular_ 
_Vesicles_, submitted.

@@

## Contents
```
    .
    ├── ...
    ├── /inst
    │    ├── /manuscript
    │         ├── /components                 # Contains required components for building the manuscript
    │         ├── /figures                    # Contains .svg and .csv files used to make some figures
    │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
    │         ├── README.Rmd                  # Rmarkdown file to produce README.md
    │         ├── README.md                   # Description of /inst/manuscript directory
    │         ├── candidaev_manuscript.docx   # Full manuscript text and figure legends as submitted
    │         ├── candidaev_figures.pdf       # Main figures and table as submitted
    │         ├── candidaev_figures.Rmd       # Rmarkdown file to produce candidaev_figures.pdf
    │         ├── candidaev_supplement.pdf    # Supplementary figures and tables as submitted
    │         └── candidaev_supplement.Rmd    # Rmarkdown file to produce candidaev_supplement.pdf
    └── ...
